Deriving an Executable Model of a Data Stream Protocol from its Specification

### 2009-12-01 papers/ModelBasedTestCaseGenerationDataStreamProtocol/paper.tex
New brutal/punchy abstract.

  Sensor equipped devices typically communicate with a streaming
  packet-based network protocol.  The communication is focused on
  controlling the sensors and reporting the sensors measurements.  The
  \STSB is an example of such a device: it communicates with an
  arbitrary computer system, the \STPU, over a USB bus using a
  streaming packet-based protocol.  The \STU is a custom-designed, but
  inexpensive, sensor platform: it is composed by a one or more \STSBs
  paired with a general-purpose small-scale compute node, the \STPU
  (including everything from PDAs to powerful touchscreen-based
  portable computers).  There are over a dozen sensors on the \STSB
  itself, and new sensors can be added either using expansion slots on
  the \STSB, or adding them directly to the USB bus.  A third-party
  low-level library creates and parses generic USB communication
  packets; the library has been provided by the vendor of the USB chip
  vendor, the USB chip that has been used in the \STSB.

  A custom medium-level Java driver creates and parses the \STSB
  streaming communication packets.  The driver is formally specified,
  validated and verified with rigorous unit testing, both hand made
  and automatically generated.  Because of this process and
  combination of technologies, we are able to verify a real \ST and a
  simulated one as well.  The system has been developed concurrently
  with the protocol specification and the real \STSB, the boards have
  not been available until the last months of development.  The
  protocol model is itself an executable stream simulator that can be
  used to develop new \ST user applications without having the \ST
  hardware at all.  Consequently, from this single specification, we
  are able to test that the \ST hardware communicates as expected,
  that our \ST simulator communicates as expected, and simulate the
  \ST protocol stream itself.

>>>>

%  A punchy abstract that makes the reader want to know more.

  Agile people hate formal people.  Formal people think agile people
  are flakes.  These two worlds do not talk to or learn from each
  other.  This is bullshit.  This paper summarizes a complex case
  study which shows that it is not only possible, but tasty, to
  combine the garlic of formal methods and the chocolate of agile
  programming.

%   Sensor equipped devices typically communicate with a streaming
%   packet-based network protocol.  The communication is focused on
%   controlling the sensors and reporting the sensors measurements.  The
%   \STSB is an example of such a device: it communicates with an
%   arbitrary computer system, the \STPU, over a USB bus using a
%   streaming packet-based protocol.  The \STU is a custom-designed, but
%   inexpensive, sensor platform: it is composed by a one or more \STSBs
%   paired with a general-purpose small-scale compute node, the \STPU
%   (including everything from PDAs to powerful touchscreen-based
%   portable computers).  There are over a dozen sensors on the \STSB
%   itself, and new sensors can be added either using expansion slots on
%   the \STSB, or adding them directly to the USB bus.  A third-party
%   low-level library creates and parses generic USB communication
%   packets; the library has been provided by the vendor of the USB chip
%   vendor, the USB chip that has been used in the \STSB.

%   A custom medium-level Java driver creates and parses the \STSB
%   streaming communication packets.  The driver is formally specified,
%   validated and verified with rigorous unit testing, both hand made
%   and automatically generated.  Because of this process and
%   combination of technologies, we are able to verify a real \ST and a
%   simulated one as well.  The system has been developed concurrently
%   with the protocol specification and the real \STSB, the boards have
%   not been available until the last months of development.  The
%   protocol model is itself an executable stream simulator that can be
%   used to develop new \ST user applications without having the \ST
%   hardware at all.  Consequently, from this single specification, we
%   are able to test that the \ST hardware communicates as expected,
%   that our \ST simulator communicates as expected, and simulate the
%   \ST protocol stream itself.
